Ultrafast Control of Spin-Spin Interactions in Two-Dimensional Magnetic Systems: Kane-Mele-Hubbard Model

### 2019-03-07 Paper/paper.tex
v4.2

\begin{figure}[t]
\centering
\includegraphics[width=0.6\columnwidth]{kmh.png}
\caption{A honycomb cell with NN hopping $t_1$, NNN hopping $t_2$ and intrinsic SOI $\Delta$. $\nu_{ij} = \pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$).}
\label{fig1}
\vspace*{-6pt}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.6\columnwidth]{kmh.png}
\caption{A honeycomb cell with NN hopping $t_1$, NNN hopping $t_2$, intrinsic SOI $\Delta$, and $\nu_{ij} = \pm 1$ for clockwise and counter-clockwise hoping.}
\label{fig1}
\vspace*{-6pt}
\end{figure}
